---
title: 'Analyses'
author: 
output: 
  github_document:
always_allow_html: true
editor_options: 
  chunk_output_type: console
---

```{r "setup", include=FALSE}
library(knitr)
opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.align = "center",
                      fig.path=('../../report/figures/'))
options(scipen = 1, digits = 2)
library(rmarkdown)
```

# Scripts


# Required Packages &amp; Reproducibility
```{r "env", message=FALSE, warning=F}
rm(list=ls())
source(here::here("src/lib/functions.R"))
```

# Pre-Registered Analyses

```{r "data for analyses"}
load(here("data/intermediate/clean_data.RData"))
```

Next, we automatically extract a `.md` file for the online appendix, as well as a  latex table for the manuscript. 
We are using jinja2 template [src/analysis/table_descriptives.tex.j2](table.tex.j2) which is called with a json string containing the data.
To replicate, make sure `env/bin/pip install -U j2cli` is installed via your command line.

```{r "Table with Descriptives"}
source(here("src/analysis/descriptive-information-overview.R"))
table2 <- knitr::kable(descr, digits=2)
fn <- here("report/figures/table_descriptives.tex")
cat("# Table: Descriptive Information of Variables under Study \n\n", file=fn)
cat(table2, file=fn, sep="\n", append=T)

methodnames <- setNames(as.list(descr$Variables), descr$Variables)
table <- purrr::map(descr, .f= ".") 
#render_j2(here("src/analysis/table_descriptives.tex.j2"), here("report/figures/table_descriptives.tex"),
#          data=list(data=table, methods=methodnames))
rm(descr, methodnames, table, fn, table2)
```

## Pre-Registered Hypotheses 
```{r "h-pre-reg", fig.align="center", fig.height=10, fig.width=10}
source(here("src/analysis/pre-registered.R"))
p

kbl(df, booktabs =T, caption = "Effect of Identifying as Female for Pre-Registered Hypothesis") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "10cm") %>%
  column_spec(2, width = "2cm")  %>%
  column_spec(3, width = "4cm") %>%
  column_spec(4, width = "4cm")
```

## Explorative Results
```{r "explorative", fig.align="center",  fig.height=10, fig.width=10}
source(here("src/analysis/explorative.R"))
p_disc
p_career
```